Storing messages with multipartite neural cliques

### 2014-06-30 Articles/article.tex
correction Xi

\usepackage[english]{babel} 
\usepackage[T1]{fontenc}
%\usepackage{fullpage}
\usepackage[]{bbm}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
%\usepackage{pstricks}
\usepackage{float}
\usepackage[autolanguage]{numprint}
%\usepackage[squaren,Gray]{SIunits}
%\usepackage{tikz}
%
%\usepackage[style=numeric,backend=bibtex]{biblatex}
\pagestyle{myheadings}

\title{Storing messages with multipartite neural cliques}
\author{???}
\date{
	}
%

@@

	 \begin{abstract}
	 ???
	 \end{abstract}

	\keywords{associative memory, error correcting code}

@@

		\subsection{Analytical results}

@@

	\subsection{Simulations}
		Improves the retrieval rate for multiple iterations and/or corrupted messages.

@@

	\begin{figure}
		\includegraphics[width=8.5cm]{comparaison_regles_pool5_a2c4l512e2}
		\caption{2 activities per cluster, 4 clusters, 512 neurons per cluster, two erasures, each point is the mean of 5 networks with 1000 sampled messages, analytical result in continuous black}
		\end{figure}

	\begin{figure}
		\includegraphics[width=8.5cm]{remplacement_figure3g1}
		\caption{2 activities per cluster, 4 clusters, 512 neurons per cluster, one erroneous cluster, each point is the mean of 5 networks with 1000 sampled messages, analytical result in continuous black}
	\end{figure}

	\newpage
	a
	\newpage
	Spéculations en Français :

@@

	$P(n_{ge} = (c - c_e) + \gamma + x) = {c_e - 1 \choose x} d^x (1-d)^{c_e-1-x}$

@@

	\begin{align*}
	P_{retrieve} = \left [ \sum_{n = 1}^{a(c-1) + \gamma} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{gc} = n)^k P(n_{gc} > n)^{a-k} \right ]\left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-a} \right ]^{c - c_e} \\ \times \left [ \sum_{n = 1}^{a(c-1) +\gamma} \left[ \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k} \right ] \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-2a} \left [ \sum_{x=0}^{n-1} P(n_{abc} = x) \right]^a \right ]^{c_e}
	\end{align*}

@@

	%Marche mieux pouur de petits c --> le faire sur le sparse ?
	\nocite{*}
	\bibliographystyle{plain} % Le style est mis entre crochets.
         \bibliography{bibli.bib}
\end{document}

>>>>

\usepackage[english]{babel} 
\usepackage[T1]{fontenc}
%\usepackage{fullpage}
\usepackage[]{bbm}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
%\usepackage{pstricks}
\usepackage{float}
\usepackage[autolanguage]{numprint}
\usepackage[affil-it]{authblk}
%\usepackage[squaren,Gray]{SIunits}
%\usepackage{tikz}
%
%\usepackage[style=numeric,backend=bibtex]{biblatex}
\pagestyle{myheadings}

\title{Storing messages with multipartite neural cliques}
\author[]{Nissim Zerbib}
\affil{Département d'Informatique, École normale supérieure, Paris, France}

\author[]{Vincent Gripon}
\affil{Département d'Électronique, Télécom Bretagne, Brest, France}

\author{?}

\date{
	}
%

@@

	 \begin{abstract}
	 	We extend recently introduced associative memories based on cliques to multipartite cliques. We propose a variant of the classic retrieving rule. We study their relative performance for retrieving partially erased and corrupted messages. We provide both analytical and simulation results showing improvements of capacity.
	 \end{abstract}

	\keywords{associative memory, error correcting code, cliques, multipartite cliques, neural networks}

@@

	\subsection{Retrieving partially erased messages}

	\subsubsection{Analytical result}

@@

	\subsubsection{Simulations}
		Improves the retrieval rate for multiple iterations and/or corrupted messages.

@@

	\begin{figure}
		\includegraphics[width=8.5cm]{remplacement_figure2g1} %{comparaison_regles_pool5_a2c4l512e2}
		\caption{2 activities per cluster, 4 clusters, 512 neurons per cluster, two erasures, each point is the mean of 5 networks with 1000 sampled messages, analytical result in continuous black}
		\end{figure}

	\subsection{Retrieving corrupted messages}
	\begin{figure}
		\includegraphics[width=8.5cm]{remplacement_figure3g1}
		\caption{2 activities per cluster, 4 clusters, 512 neurons per cluster, one erroneous cluster, each point is the mean of 5 networks with 1000 sampled messages, analytical result in continuous black}
	\end{figure}

	Spéculations en Français :

@@

	$P(n_{ge} = (c - c_e) + x) = {c_e - 1 \choose x} d^x (1-d)^{c_e-1-x}$

@@

	%\begin{align*}
	$P_{retrieve} = \left [ \sum_{n = 1}^{a(c-1) + \gamma} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{gc} = n)^k P(n_{gc} > n)^{a-k} \right ] P(n_{bc} < n)^{l-a} \right ]^{c - c_e} \\ \times \left [ \sum_{n = 1}^{a(c-1) +\gamma} \left[ \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k} \right ] P(n_{bc} < n)^{l-2a} P(n_{abc} < n)^a \right ]^{c_e}
	$
	%\end{align*}

@@

	%Marche mieux pouur de petits c --> le faire sur le sparse ?
	\nocite{*}
	\bibliographystyle{numeric} % Le style est mis entre crochets.
         \bibliography{bibli.bib}
\end{document}
